Manuscript progress report

### 2024-01-24 Docs/manuscript.Rmd
again, fix the figures

rand_id <- sample(501:600, size = 2)
```

@@

```{r fig_sim, fig.height=8, fig.width=5}
ggarrange(fig_fgfpca, fig_adglmm, fig_gfosr_l1, fig_gfosr_l5,
          ncol = 1, common.legend = T)
```

@@

mean_auc_adglmm <- apply(auc_adglmm, c(1, 2), mean)
colnames(mean_auc_adglmm) <- c("0.2", "0.4", "0.6", "0.8")
```
```{r auc_gfosr_l1}
for(m in 1:M){
  this_df <- pred_list_gfosr_l1[[m]]
  auc_tb <- this_df %>% 
    select(Y, starts_with("pred"), window) %>%
    group_by(window) %>%
    summarise(auc1 = get_auc(Y, pred_w1),
              auc2 = get_auc(Y, pred_w2),
              auc3 = get_auc(Y, pred_w3),
              auc4 = get_auc(Y, pred_w4)) %>%
    filter(window != 1) %>% 
    select(starts_with("auc"))
  auc_gfosr_l1[, ,m] <- as.matrix(auc_tb)

@@

rand_id <- sample(101:200, size = 2)
```

@@

```{r fig_pred_subset}
fig_fgfpca2 <- pred_subset_fGFPCA[[1]] %>%
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "fGFPCA", col = "Maximum observation time",
       x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_adglmm2 <- pred_subset_adglmm[[1]] %>% 
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "GLMMadaptive", col = "Maximum observation time",
       x = "Time", y = "")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_gfosr_l1_2 <- pred_subset_gfosr_l1[[1]] %>% 
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred_w1, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w2, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w3, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w4, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "GFOSR (L=1)", col = "Maximum observation time",
       x = "Time", y = "")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_gfosr_l5_2 <- pred_subset_gfosr_l5[[1]] %>% 
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred_w1, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w2, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w3, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w4, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "GFOSR (L=5)", col = "Maximum observation time",
       x = "Time", y = "")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))
```

```{r fig_sim2, fig.height=8, fig.width=5}
ggarrange(fig_fgfpca2, fig_adglmm2, fig_gfosr_l1_2, fig_gfosr_l5_2,
          ncol = 1, common.legend = T)
```

>>>>

rand_id <- sample(501:600, size = 4)
```

@@

```{r fig_sim, fig.height=8, fig.width=8}
ggarrange(fig_fgfpca, fig_adglmm, fig_gfosr_l1, fig_gfosr_l5,
          ncol = 1, common.legend = T)
```

@@

mean_auc_adglmm <- apply(auc_adglmm, c(1, 2), mean)
colnames(mean_auc_adglmm) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc_gfosr_l1}
for(m in 1:M){
  this_df <- pred_list_gfosr_l1[[m]]
  auc_tb <- this_df %>% 
    select(Y, starts_with("pred"), window) %>%
    group_by(window) %>%
    summarise(auc1 = get_auc(Y, pred_w1),
              auc2 = get_auc(Y, pred_w2),
              auc3 = get_auc(Y, pred_w3),
              auc4 = get_auc(Y, pred_w4)) %>%
    filter(window != 1) %>% 
    select(starts_with("auc"))
  auc_gfosr_l1[, ,m] <- as.matrix(auc_tb)

@@

rand_id <- sample(101:200, size = 4)
```

@@

```{r fig_pred_subset}
fig_fgfpca2 <- pred_subset_fGFPCA[[1]] %>%
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow = 1)+
  labs(title = "fGFPCA", col = "Maximum observation time",
       x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_adglmm2 <- pred_subset_adglmm[[1]] %>% 
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow = 1)+
  labs(title = "GLMMadaptive", col = "Maximum observation time",
       x = "Time", y = "")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_gfosr_l1_2 <- pred_subset_gfosr_l1[[1]] %>% 
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred_w1, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w2, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w3, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w4, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow=1)+
  labs(title = "GFOSR (L=1)", col = "Maximum observation time",
       x = "Time", y = "")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_gfosr_l5_2 <- pred_subset_gfosr_l5[[1]] %>% 
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred_w1, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w2, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w3, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w4, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow=1)+
  labs(title = "GFOSR (L=5)", col = "Maximum observation time",
       x = "Time", y = "")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))
```

```{r fig_sim2, fig.height=8, fig.width=8}
ggarrange(fig_fgfpca2, fig_adglmm2, fig_gfosr_l1_2, fig_gfosr_l5_2,
          ncol = 1, common.legend = T)
```
